---
title: "testing"
author: "Ray Hunter"
date: "2023-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# telling r where files are located 
library(here)
# for manipulating date and time
library(lubridate)
# might not need this, for reading in files from box to R
library(boxr)
library(camtrapR)
# making data tidy and neat 
library(dplyr)
# allows r to find metadata of photos 
library(exiftoolr)

#spatial analysis 
library(sp)
library(rgdal)
library(plotKML)
```


```{r}
#clearing list every time it runs 
rm(list = ls())
```


### Setting up Exiftool: 
* Code is hidden b/c I have already installed it and dont want to do so again every time I run this file 
* delete the single "#" symbols on each line to run that code 


```{r}
########### installing ExifTool on computer and then telling R where to find it ########
 
#  install_exiftool("/Users/rayhunter/Downloads")

########## pointing to where ExifTool is  located #############

# exiftoolPath("/usr/local/bin/ExifTool")

############ check to see if R can find Exiftool ################

# Sys.which("ExifTool")

```




### trying to set up box API so r can read images from box (not working too well) 
```{r}

# # Authenticate with Box using your API credentials
# box_auth(client_id = "qo4enkm1e1jnscbmy82a2w6dmojjbj7g", client_secret = "adqa1lqxSM4RzkV0rLIXNLoN0oJzZyjA")
# 
# 
# 
# # Specify the name of the folder you want to find the path for
# trial_data <- "trial_data"
# 
# # Search for the folder using its name
# folder <- box_ls(recursive = FALSE, query = trial_data, type = "folder")
# 
# # Print the folder path
# cat("Folder Path:", folder$path, "\n")
```







### read in the image data 

```{r}
################## raw cam trap csv file of photos ####################### 
t1_dat <- read.csv(here("trial_1.csv"))

##### modified t1 data to fit format of camtrapR ###########

t1_mod <- t1_dat %>% 
  #renaming date time 
  rename(DateTimeOriginal = DateTime) %>% 
  # renaming file name 
  rename(FileName = File) %>% 
  #creating a column called "Date" from DateTimeOriginal using lubridate package
  mutate(Date = as_date(ymd_hms(DateTimeOriginal))) %>% 
    #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
  mutate(Time = format(ymd_hms(DateTimeOriginal), format = "%H:%M:%S")) %>% 
  #selecting a specific columns 
  select(c("Station", "Species", "DateTimeOriginal", "Date", "Time", "FileName"))
```



### read in the station data 
```{r}
################ station data ################

stat_dat_raw <- read.csv(here("station_data.csv")) 

stat_dat_mod <- stat_dat_raw %>% 
  rename(Station = Camera.Number)


# # Setting existing coordinate as lat-long system
# coords <- stat_dat_mod[, c("Longitude", "Latitude")]
# coordinates(coords) <- c("Longitude", "Latitude")
# 
# 
# 
# proj4string(coords) <- CRS("+proj=longlat +datum=WGS84")
# 
# # Project the coordinates to UTM
# coords_utm <- spTransform(coords, CRS("+proj=utm +zone=auto"))
# 
# # Extract the UTM x and UTM y coordinates
# stat_dat_mod$utm_x <- coords_utm@coords[, 1]
stat_dat_mod$utm_y <- coords_utm@coords[, 2]
```






### Renaming Images 

```{r}
# file path of photos folder 
wd_images_raw <- "//Volumes/TNC_HD/trial_1/trial_1_cleaned_images"

# creating a new file path for renamed images in Working directory 
wd_images_renamed <- "/Volumes/TNC_HD/trial_1/trial_1_cleaned_images_renamed"




# fixing a time issue with raw images 
time_table <- data.frame(c(Station = "Station 6", camera = NA, timeshift = 0:0:0 0:0:0, sign = ))









# renaming photos from the indirectory and storing int he outdirectory 
renamed <- imageRename(inDir = wd_images_raw,
                       outDir = wd_images_renamed,
                       hasCameraFolders = FALSE, 
                       copyImages = TRUE)
```













## looking to see if cameras were down in the operation 

```{r}
camop_problem <- cameraOperation(CTtable = dat,
                                 stationCol = "Station ", #column containing station Id's
                                 setupCol = "Date_Set", #column using date of deployment 
                                 retrievalCol = "Date_Retrieved",
                                 writecsv = FALSE,
                                 hasProblems = TRUE, # if we have a colomn of camera malfunctions 
                                 dtaeFormat = "%d/%m/%Y" #date format in the file 
                                
                                 )

camopPlot(camOp = camop_problem)


```




### extracting data 




























```{r}

data("camtraps")
camtraps



data("recordTableSample")
recordTableSample





data("timeShiftTable")
timeShiftTable




```

