---
title: "COPR Camtrap Analysis"
author: "Ray Hunter"
date: "2023-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
# telling r where files are located 
library(here)
# for manipulating date and time
library(lubridate)
# might not need this, for reading in files from box to R
library(boxr)
library(camtrapR)
# making data tidy and neat 
library(dplyr)
# allows r to find metadata of photos 
library(exiftoolr)
#spatial analysis 
library(sp)
library(rgdal)
library(plotKML)
#statistical analysis 
library(stats)
library(unmarked)
```


```{r setup, include=FALSE}
#clearing list every time it runs 
rm(list = ls())
```





### Setting up Exiftool: 
* Code is hidden b/c I have already installed it and dont want to do so again every time I run this file 
* delete the single "#" symbols on each line to run that code 


```{r}
########### installing ExifTool on computer and then telling R where to find it ########
 
#  install_exiftool("/Users/rayhunter/Downloads")

########## pointing to where ExifTool is  located #############

# exiftoolPath("/usr/local/bin/ExifTool")

############ check to see if R can find Exiftool ################

# Sys.which("ExifTool")

```





### Read in the image csv data 

```{r}
################## Read in trial 1 csv file  ####################### 
t1_dat <- read.csv(here("data", "trial_1.csv"))

##### modified t1 data to fit format of camtrapR ###########

t1_mod <- t1_dat %>% 
  # renaming file name 
  rename(FileName = File) %>% 
    #renaming date time 
    rename(DateTimeOriginal = DateTime) %>% 
      # formatting the date time 
       mutate(DateTimeOriginal = ymd_hms(DateTimeOriginal)) %>% 
        # adding 24 hrs to station 6 b/c it was behind 1 day in the field 
        mutate(DateTimeOriginal = case_when(
          Station == "Station 6" ~ DateTimeOriginal + hours(24), TRUE ~ DateTimeOriginal)) %>%
           #creating a column called "Date" from DateTimeOriginal using lubridate package
           mutate(Date = as_date(DateTimeOriginal)) %>% 
            #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
            mutate(Time = format(DateTimeOriginal, format = "%H:%M:%S")) %>% 
              #selecting a specific columns 
              select(c("Station", "treatment", "Species", "Number", "DateTimeOriginal", "Date", "Time", "FileName")) %>% 
  filter(Station != "" )










################## Read in trial 2 csv file  ####################### 
t2_dat <- read.csv(here("data", "trial_2.csv"))

##### modified t2 data to fit format of camtrapR ###########

t2_mod <- t2_dat %>% 
  # renaming file name 
  rename(FileName = File) %>% 
  #renaming date time 
  rename(DateTimeOriginal = DateTime) %>% 
   # adding 24 hrs to station 6 b/c it was behind 1 day in the field 
  mutate(DateTimeOriginal = ymd_hms(DateTimeOriginal)) %>% 
        # adding 24 hrs to station 6 b/c it was behind 1 day in the field 
        mutate(DateTimeOriginal = case_when(
          Station == "Station 6B" ~ DateTimeOriginal + hours(24), TRUE ~ DateTimeOriginal)) %>%
  #creating a column called "Date" from DateTimeOriginal using lubridate package
  mutate(Date = as_date(DateTimeOriginal)) %>% 
    #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
  mutate(Time = format(DateTimeOriginal, format = "%H:%M:%S")) %>% 
  #selecting a specific columns 
  select(c("Station", "treatment", "Species","Number", "DateTimeOriginal", "Date", "Time", "FileName")) 
    





################## Read in trial 3 csv file  ####################### 
t3_dat <- read.csv(here("data", "trial_3.csv"))

##### modified t3 data to fit format of camtrapR ###########

t3_mod <- t3_dat %>% 
  #renaming date time 
  rename(DateTimeOriginal = DateTime) %>% 
  # renaming file name 
  rename(FileName = File) %>% 
  #creating a column called "Date" from DateTimeOriginal using lubridate package
  mutate(Date = as_date(ymd_hms(DateTimeOriginal))) %>% 
    #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
  mutate(Time = format(ymd_hms(DateTimeOriginal), format = "%H:%M:%S")) %>% 
  #selecting a specific columns 
  select(c("Station", "treatment", "Species", "Number", "DateTimeOriginal", "Date", "Time", "FileName")) 
     











################## Read in trial 4 csv file  ####################### 
t4_dat <- read.csv(here("data", "trial_4.csv"))

##### modified t3 data to fit format of camtrapR ###########

t4_mod <- t4_dat %>% 
  #renaming date time 
  rename(DateTimeOriginal = DateTime) %>% 
  # renaming file name 
  rename(FileName = File) %>% 
  #creating a column called "Date" from DateTimeOriginal using lubridate package
  mutate(Date = as_date(ymd_hms(DateTimeOriginal))) %>% 
    #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
  mutate(Time = format(ymd_hms(DateTimeOriginal), format = "%H:%M:%S")) %>% 
  #selecting a specific columns 
  select(c("Station", "treatment", "Species", "Number", "DateTimeOriginal", "Date", "Time", "FileName")) 


```



### Merging all trial data frames 
```{r}

# all species observation data
all_mod  <- rbind(t1_mod, t2_mod, t3_mod, t4_mod) %>% 
  # getting rid of an error
  filter(Station != "") %>% 
  # creating a column saying whether its a rodent or not 
  mutate(rodent = ifelse(Species %in% c("Woodrat", "Black rat", "Mouse"), TRUE, FALSE))  
 


# just rodent data 
rod_mod <- all_mod %>% 
  filter(rodent == "TRUE")

```



### Read in the station data 

```{r}
################ station data ################

stat_dat_raw <- read.csv(here("data", "station_data.csv"))

#modified data and fixing times using lubridate so that dates are read as dates and not characters 
stat_dat_mod <- stat_dat_raw %>% 
  mutate(Treatment = str_trim(Treatment)) %>% 
  mutate(Date_Installed = mdy(Date_Installed)) %>% 
  mutate(Date_Retrieved = mdy(Date_Retrieved)) %>% 
  mutate(Problem1_from = mdy(Problem1_from)) %>% 
    mutate(Problem1_to = mdy(Problem1_to))

#removing rows (if needed)
stat_dat_mod <- stat_dat_mod[-c(49:72), ]  
    
  
  
  

```

### Camera Operability 
```{r}
#this step is necessary to put in a camera operation table telling camtrapR when the cameras were running and if there was any issues. Ex; if camera #12 was down for a couple days, you would insert it in stat_dat_mod and then cameraOperations would create a table saying it was down. Even though we didnt have any issues with our cameras, we still had to create a table for this cause its necessary in following steps
camop_problem <- cameraOperation( CTtable = stat_dat_mod,
                      stationCol = "Station",
                      setupCol = "Date_Installed",
                      retrievalCol = "Date_Retrieved",
                      hasProblems = TRUE,
                      dateFormat = "ymd"
                      
)





```






### Separate Detections by Timeperiods 

```{r}
# creating a data frame that shows observations based off images taken > 3 minutes apart  
# some images were taken at the same time durin the bursts (ex: two photos of the 3 photo busrst were taken on the same second) which causes the assessTemporalIndependence function to make duplicates of records. so we need to get rid of them in the next step after creating the ind_recs data frame 
ind_recs <- camtrapR:::assessTemporalIndependence(intable = rod_mod, 
                                                       deltaTimeComparedTo = "lastIndependentRecord",
                                                       columnOfInterest = "Species",
                                                       cameraCol = "Station",
                                                       camerasIndependent = TRUE,
                                                       stationCol = "Station",
                                                       minDeltaTime = 3,
                                                  
                                                   
)
```


```{r}

#removing independent records duplicates 
ind_recs_mod <- ind_recs[!duplicated(ind_recs[c("Species", "DateTimeOriginal", "Station", "delta.time.secs")]), ]


```


### Reports
```{r}
#creating summary reports 
report <- surveyReport(recordTable = ind_recs_mod,
                       CTtable = stat_dat_mod,
                       CTDateFormat = "ymd",
                       speciesCol = "Species",
                       setupCol = "Date_Installed",
                       retrievalCol = "Date_Retrieved",
                       recordDateTimeCol = "DateTimeOriginal")


report1 <- report$species_by_station 
report2 <- report$events_by_species
report3 <- report$events_by_station
```






### Wood Rat Detection History 
```{r}
#here we create a detection history for each species of interest. Says if a species was observed or not during each day 
woodrat_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_mod,
                       camOp = camop_problem,
                       species = "Woodrat",
                       stationCol = "Station",
                       speciesCol = "Species",
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       occasionLength = 1,
                       occasionStartTime = 0, 
                       day1 = "station",
                       includeEffort = TRUE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
  #adding the station names
  rownames_to_column("Station" ) %>% 
  mutate(detection_history.o1 = ifelse(effort.o1 == 0, NA, detection_history.o1)) %>% 
 mutate(detection_history.o2 = ifelse(effort.o2 == 0, NA, detection_history.o2)) %>% 
  mutate(detection_history.o3 = ifelse(effort.o3 == 0, NA, detection_history.o3)) %>% 
  mutate(detection_history.o4 = ifelse(effort.o4 == 0, NA, detection_history.o4)) %>% 
  mutate(detection_history.o5 = ifelse(effort.o5 == 0, NA, detection_history.o5)) %>% 
  mutate(detection_history.o6 = ifelse(effort.o6 == 0, NA, detection_history.o6)) %>% 
  mutate(detection_history.o7 = ifelse(effort.o7 == 0, NA, detection_history.o7)) %>% 
  mutate(detection_history.o8 = ifelse(effort.o8 == 0, NA, detection_history.o8)) %>% 
  mutate(detection_history.o9 = ifelse(effort.o9 == 0, NA, detection_history.o9)) %>% 
  mutate(detection_history.o10 = ifelse(effort.o10 == 0, NA, detection_history.o10)) %>% 
  mutate(detection_history.o11 = ifelse(effort.o11 == 0, NA, detection_history.o11)) %>% 
  mutate(detection_history.o12 = ifelse(effort.o12 == 0, NA, detection_history.o12)) 


#combined df in tidy format
wr_hist_mod <- woodrat_hist  %>%
  #selecting just the detection history 
  select(Station:detection_history.o12) %>%
  #tidy format 
 pivot_longer(cols = c(detection_history.o1:detection_history.o12),
               names_to = "day",
               values_to = "detection") %>%
  #combining both DF's in tiday format
  merge( stat_dat_mod[, c("Station", "Treatment")], by = "Station", all.x = TRUE) %>%
   #creating a species name
  mutate(Species = "Woodrat")
  


#creating a summary df
wr_hist_sum <- wr_hist_mod %>% 
  #grouping byt station and treatment for summary 
  group_by(Station, Treatment, Species) %>%
  #taking the means 
  summarise(detection_prob = mean(detection, na.rm = TRUE))
```




### Black Rat Detection History 
```{r}
#here we create a detection history for each species of interest. Says if a species was observed or not during each day 
blackrat_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_mod,
                       camOp = camop_problem,
                       species = "Black rat",
                       stationCol = "Station",
                       speciesCol = "Species",
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       occasionLength = 1,
                       occasionStartTime = 0, 
                       day1 = "station",
                       includeEffort = TRUE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
  #adding the station names
  rownames_to_column("Station" ) %>% 
  #making detection history NA values when effort = 0
    mutate(detection_history.o1 = ifelse(effort.o1 == 0, NA, detection_history.o1)) %>% 
 mutate(detection_history.o2 = ifelse(effort.o2 == 0, NA, detection_history.o2)) %>% 
  mutate(detection_history.o3 = ifelse(effort.o3 == 0, NA, detection_history.o3)) %>% 
  mutate(detection_history.o4 = ifelse(effort.o4 == 0, NA, detection_history.o4)) %>% 
  mutate(detection_history.o5 = ifelse(effort.o5 == 0, NA, detection_history.o5)) %>% 
  mutate(detection_history.o6 = ifelse(effort.o6 == 0, NA, detection_history.o6)) %>% 
  mutate(detection_history.o7 = ifelse(effort.o7 == 0, NA, detection_history.o7)) %>% 
  mutate(detection_history.o8 = ifelse(effort.o8 == 0, NA, detection_history.o8)) %>% 
  mutate(detection_history.o9 = ifelse(effort.o9 == 0, NA, detection_history.o9)) %>% 
  mutate(detection_history.o10 = ifelse(effort.o10 == 0, NA, detection_history.o10)) %>% 
  mutate(detection_history.o11 = ifelse(effort.o11 == 0, NA, detection_history.o11)) %>% 
  mutate(detection_history.o12 = ifelse(effort.o12 == 0, NA, detection_history.o12)) 
 






#combined df in tidy format
br_hist_mod <- blackrat_hist  %>%
  #selecting just the detection history 
  select(Station:detection_history.o12) %>%
  #tidy format 
 pivot_longer(cols = c(detection_history.o1:detection_history.o12),
               names_to = "day",
               values_to = "detection") %>%
  #combining both DF's in tiday format
  merge( stat_dat_mod[, c("Station", "Treatment")], by = "Station", all.x = TRUE) %>%
   #creating a species name
  mutate(Species = "Black rat")




#creating a summary df
br_hist_sum <- br_hist_mod %>% 
  #grouping byt station and treatment for summary 
  group_by(Station, Treatment, Species) %>%
  #taking the means 
  summarise(detection_prob = mean(detection, na.rm = TRUE))
```




### Mouse Detection History 

```{r}
#here we create a detection history for each species of interest. Says if a species was observed or not during each day 
mouse_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_mod,
                       camOp = camop_problem,
                       species = "Mouse",
                       stationCol = "Station",
                       speciesCol = "Species",
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       occasionLength = 1,
                       occasionStartTime = 0, 
                       day1 = "station",
                       includeEffort = TRUE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
  #adding the station names
  rownames_to_column("Station" ) %>% 
    #making detection history NA values when effort = 0
    mutate(detection_history.o1 = ifelse(effort.o1 == 0, NA, detection_history.o1)) %>% 
 mutate(detection_history.o2 = ifelse(effort.o2 == 0, NA, detection_history.o2)) %>% 
  mutate(detection_history.o3 = ifelse(effort.o3 == 0, NA, detection_history.o3)) %>% 
  mutate(detection_history.o4 = ifelse(effort.o4 == 0, NA, detection_history.o4)) %>% 
  mutate(detection_history.o5 = ifelse(effort.o5 == 0, NA, detection_history.o5)) %>% 
  mutate(detection_history.o6 = ifelse(effort.o6 == 0, NA, detection_history.o6)) %>% 
  mutate(detection_history.o7 = ifelse(effort.o7 == 0, NA, detection_history.o7)) %>% 
  mutate(detection_history.o8 = ifelse(effort.o8 == 0, NA, detection_history.o8)) %>% 
  mutate(detection_history.o9 = ifelse(effort.o9 == 0, NA, detection_history.o9)) %>% 
  mutate(detection_history.o10 = ifelse(effort.o10 == 0, NA, detection_history.o10)) %>% 
  mutate(detection_history.o11 = ifelse(effort.o11 == 0, NA, detection_history.o11)) %>% 
  mutate(detection_history.o12 = ifelse(effort.o12 == 0, NA, detection_history.o12)) 
 

#combined df in tidy format
mou_hist_mod <- mouse_hist  %>%
  #selecting just the detection history 
  select(Station:detection_history.o12) %>%
  #tidy format 
 pivot_longer(cols = c(detection_history.o1:detection_history.o12),
               names_to = "day",
               values_to = "detection") %>%
  #combining both DF's in tiday format
  merge( stat_dat_mod[, c("Station", "Treatment")], by = "Station", all.x = TRUE) %>%
   #creating a species name
  mutate(Species = "Mouse")


#creating a summary df
mou_hist_sum <- mou_hist_mod %>% 
  #grouping byt station and treatment for summary 
  group_by(Station, Treatment, Species ) %>%
  #taking the means 
  summarise(detection_prob = mean(detection, na.rm = TRUE))

```





### combined 
```{r}



############ combining and summarizing each data frame into one  


rodent_sum <- rbind(wr_hist_sum, br_hist_sum, mou_hist_sum)

```




##################### Occupancy modeling ####################

```{r}
#assigning a list of covariates 
covs <- as.data.frame(stat_dat_mod$Treatment)
names(covs) <- "Treatment"

UFO_wr <- unmarkedFrameOccu(y = woodrat_hist[,2:13], siteCovs = covs)
summary(UFO_wr)


########## model 1: no variation across habitat ###############

m1 <- occu(~1 ~1, data = UFO_wr)


m1.psi <- backTransform(m1, type = "state")
m1.psi

m1.p <- backTransform(m1, type = "det")
m1.p


m1CI.psi <- confint(m1.psi)
m1CI.psi


m1CI.p <- confint(m1.p)
m1CI.p


### model 2: occupancy varies across habitat  #######

m2 <- occu(~1 ~Treatment, data = UFO_wr)
m2


#################predicting

preds <- data.frame(Treatment = c("control", "PB","PB + fox"))


#use the new data to make predicitons based on the model for occupancy
fits.m2.psi <- predict(m2, type = "state", newdata = preds, appendData = TRUE) 
fits.m2.psi$type <- "psi"
fits.m2.psi

#same but for detection
fits.m2.p <- predict(m2, type = "det", newdata = preds, appendData = TRUE) 
fits.m2.p$type <- "p"
fits.m2.p

#combine
fits.m2 <- rbind(fits.m2.psi, fits.m2.p)
fits.m2




### model 3: occupancy varies across habitat  #######

m3 <- occu(~Treatment ~1, data = UFO_wr)
m3

#use the new data to make predicitons based on the model for occupancy
fits.m3.psi <- predict(m3, type = "state", newdata = preds, appendData = TRUE) 
fits.m3.psi$type <- "psi"
fits.m3.psi

#same but for detection
fits.m3.p <- predict(m3, type = "det", newdata = preds, appendData = TRUE) 
fits.m3.p$type <- "p"
fits.m3.p

#combine
fits.m3 <- rbind(fits.m3.psi, fits.m3.p)
fits.m3



#### AIC values #######

AIC <- data.frame(Model = c("m1", "m2", "m3"),
                  AIC = c(m1@AIC, m2@AIC, m3@AIC))
AIC



```


############## Occ Modeling #2 ################
```{r}
#creating list of covariates 
covs2 <- stat_dat_mod[ ,6:12]

dets_wr <- woodrat_hist[,2:13]

UFO2_wr <- unmarkedFrameOccu(y = dets_wr, siteCovs = covs2)
summary(UFO2_wr)



 #### standardizing the covariates
UFO2_wr@siteCovs$Percent_Canopy_Cover <- scale(UFO2_wr@siteCovs$Percent_Canopy_Cover)
UFO2_wr@siteCovs$Percent_Leaf_Litter <- scale(UFO2_wr@siteCovs$Percent_Leaf_Litter)
UFO2_wr@siteCovs$Percent_Bare <- scale(UFO2_wr@siteCovs$Percent_Bare)
UFO2_wr@siteCovs$Percent_Woody_Debris <- scale(UFO2_wr@siteCovs$Percent_Woody_Debris)
UFO2_wr@siteCovs$Distance_to_Water_.m. <- scale(UFO2_wr@siteCovs$Distance_to_Water_.m.)
UFO2_wr@siteCovs$Distance_to_Building_.m. <- scale(UFO2_wr@siteCovs$Distance_to_Building_.m.)
```


```{r}

################ Model 1: no vairation in detection or habitat ################
fm1<- occu(formula = ~ 1 
                     ~ 1,
           data = UFO2_wr)

# backTransform(fm1, type = "state")
# backTransform(fm1, type = "det")


################ Model 2: Datection ~ Treantment, Occupancy ~ dist. to water and building  ################

fm2 <- occu(formula = ~ Treatment 
                      ~  Distance_to_Water_.m. + Distance_to_Building_.m.,
            data = UFO2_wr)


# fm2




################ Model 3: Datection ~ Treantment, Occupancy ~ dist. to water and building  ################

fm3 <- occu(formula = ~ Treatment  + Percent_Canopy_Cover
                      ~  Distance_to_Water_.m. + Distance_to_Building_.m.,
            data = UFO2_wr)

# fm3




################ Model 4:   ################

fm4 <- occu(formula = ~ Treatment  + Percent_Woody_Debris + Distance_to_Building_.m.
                      ~ Percent_Woody_Debris + Distance_to_Water_.m. + Distance_to_Building_.m.,
            data = UFO2_wr)

fm4
```



### fitting 
```{r}
fit <- fitList('psi(.)p(.)' = fm1,
               'psi(Distance_to_Water_.m. + Distance_to_Building_.m.)p(Treatment)' = fm2,
               'psi(Distance_to_Water_.m. + Distance_to_Building_.m.)p(Treatment + Percent_Canopy_Cover)' = fm3,
               'psi(Percent_Woody_Debris + Distance_to_Water_.m. + Distance_to_Building_.m.)p(Treatment  +
                Percent_Woody_Debris + Distance_to_Building_.m.)' = fm4
               )

modSel(fit)
```
#### dredge it 
```{r}
# full <- occu(formula = ~ Treatment  + Percent_Canopy_Cover + Distance_to_Water_.m. + Distance_to_Building_.m. +
#                           Percent_Leaf_Litter + Percent_Woody_Debris
#                        ~ Percent_Canopy_Cover + Distance_to_Water_.m. + Distance_to_Building_.m. +
#                           Percent_Leaf_Litter + Percent_Woody_Debris,
#              data = UFO2_wr)
# 
# dredge_list <- MuMIn::dredge(full,
#                     rank = "AIC")
```







### ANOVA
```{r}
wr_aov <- aov(detection_prob ~ Treatment, data = wr_hist_sum)
summary(wr_aov)

TukeyHSD(wr_aov)
```
```{r}
ggplot(wr_aov, aes(Treatment, detection_prob)) +
  geom_boxplot()


ggline(wr_aov, x = "Treatment", y="detection_prob", main="Mean and 95% CI for three speceis for penguins", 
       add=c("mean_ci"), color="dark gray", 
       ylab="Body Mass (g)", xlab="Species", point.color="black")
```













### map of species detections 
```{r}
#make a map of species detections
#change "speciestoShow" to the species of interest
#you can add a polgyon of your area of interest, or export this to a Shapefile to explore in GIS
spec_map <- detectionMaps(CTtable = stat_dat_mod,
                           recordTable = ind_recs,
                           Xcol = "Longitude",
                           Ycol = "Latitude",
                           stationCol = "Station",
                           speciesCol = "Species",
                           speciesToShow = "Rat",
                           printLabels = FALSE,
                           richnessPlot = FALSE,
                           speciesPlots = TRUE,
                           addLegend = TRUE
)
```
### daily activity rates 
```{r}
#look at daily activity rates
activityDensity(recordTable = ind_recs, species = "Rabbit")
activityRadial(recordTable = ind_recs,
               species = "Rabbit",
               allSpecies = FALSE,
               speciesCol = "Species",
               recordDateTimeCol = "DateTimeOriginal",
               plotR = TRUE,
               writePNG = FALSE,
               lwd = 3,
               rp.type = "p", # plot type = polygon
               poly.col = gray(0.5, alpha = 0.5) # optional. remove for no fill
)
```





### extracting data 


















### sample data sets 

```{r}
data("camtraps")

data("recordTableSample")

data("timeShiftTable")
```

