---
title: "COPR Camtrap Analysis"
author: "Ray Hunter"
date: "2023-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#organizing/wrangling data
library(tidyverse)
library(janitor)
library(dplyr)
#adjusting dates
library(lubridate)
# telling r where files are located 
library(here)
#statistical analysis 
library(camtrapR)
library(stats)
library(MuMIn)
library(unmarked)
```


```{r setup, include=FALSE}
#clearing list every time it runs 
rm(list = ls())
```

Github:

https://github.com/ramhunte/tnc_internship-.git



## Resources Used:

### Camtrap R: 
* Vignettes (included in the folder here)

* youtube 5 part series Scott Burnett https://www.youtube.com/@scottburnett8242

#### the first viedo or two that he does is a bit confusing as a lot of the stuff he is doing is designed to read camera image metadata and create a csv file from it, which we did not do. Also it revolves around ####3

* google groups: https://groups.google.com/g/camtrapr


### Occupancy Modeling: 
* smart occupancy dude: https://www.youtube.com/watch?v=tj_OCO77_sc







### Read in the image csv data and wrangle 

```{r}
### read in raw data from each trial 
t1_dat <- read.csv(here("data", "trial_1.csv"))
t2_dat <- read.csv(here("data", "trial_2.csv"))
t3_dat <- read.csv(here("data", "trial_3.csv"))
t4_dat <- read.csv(here("data", "trial_4.csv"))
t5_dat <- read.csv(here("data", "trial_5.csv"))
t6_dat <- read.csv(here("data", "trial_6.csv"))

#join into 1 data frame 
all_mod <- rbind(t1_dat, t2_dat, t3_dat, t4_dat, t5_dat, t6_dat) %>% 
  #renaming file
  rename(FileName = File) %>% 
    #renaming date time 
    rename(DateTimeOriginal = DateTime) %>% 
      # formatting the date time using lubridate to be recognized as a date time and not character
       mutate(DateTimeOriginal = ymd_hms(DateTimeOriginal)) %>% 
        # adding 24 hrs to station 6 and 6B it was behind 1 day in the field b/c field cameras were off. Only necessary to do this step if camera times were set incorrect
        mutate(DateTimeOriginal = case_when(
          Station == c("Station 6") ~ DateTimeOriginal + hours(24), TRUE ~ DateTimeOriginal)) %>%
         mutate(DateTimeOriginal = case_when(
          Station == c("Station 6B") ~ DateTimeOriginal + hours(24), TRUE ~ DateTimeOriginal)) %>%
           #creating a column called "Date" from DateTimeOriginal using lubridate package
           mutate(Date = as_date(DateTimeOriginal)) %>% 
            #creating a column called "Time" from DateTimeOriginal using lubrdiate package 
            mutate(Time = format(DateTimeOriginal, format = "%H:%M:%S")) %>% 
              #selecting  specific columns of interest
              select(c("Station", "treatment", "Species", "Number", "DateTimeOriginal", "Date", "Time", "FileName")) %>% 
  #cleaning the station name of spaces
   mutate(Station = str_trim(Station)) %>% 
  filter(Station != "")
  

### new df with just the rodents #####
rod_mod <- all_mod %>% 
  filter(Species %in% c("Woodrat", "Black rat", "Mouse"))
```




### Independent Records: Separate Detections by Timeperiods using camtrpR

```{r}
# creating a data frame that shows observations based off images taken > 10 minutes apart  
# some images were taken at the same time during the bursts (ex: 2 out of the 3 photo busrst were taken on the same second) which causes the assessTemporalIndependence function to make duplicates of records. so we need to get rid of them in the next step after creating the ind_recs data frame 
ind_recs <- camtrapR:::assessTemporalIndependence(intable = rod_mod, 
                                                       deltaTimeComparedTo = "lastIndependentRecord",
                                                       columnOfInterest = "Species",
                                                       cameraCol = "Station",
                                                       camerasIndependent = TRUE,
                                                       stationCol = "Station",
                                                       minDeltaTime = 10,
                                                  
                                                  
                                                   
)


#removing independent records duplicates to prevent double counting  
ind_recs <- ind_recs[!duplicated(ind_recs[c("Species", "DateTimeOriginal", "Station", "delta.time.secs")]), ]


```


############## Station Data #########################

```{r}
### reading in station data 
stat_dat_multi <- read.csv(here("data", "master_sheet.csv")) %>% 
  # using lubridate to format dates
  mutate(Date_Installed = mdy(Date_Installed)) %>% 
  mutate(Date_Retrieved = mdy(Date_Retrieved)) %>% 
  #columns with camera operation problems. required for the next step even if your cameras functioned fine the whole time. This basically just tells camtrapR when a cameras wasnt working
  mutate(Problem1_from = mdy(Problem1_from)) %>% 
    mutate(Problem1_to = mdy(Problem1_to))



#this step is necessary to put in a camera operation table telling camtrapR when the cameras were running and if there was any issues. Ex; if camera #12 was down for a couple days, you would insert it in stat_dat_multi and then cameraOperations would create a table saying it was down.I entered this data for downed cameras in the column Problem1_from and Problem1_to. Even if you dont have any issues with your cameras, we still have to create a table for this cause its necessary in following steps. if there is not problems in the problems columns, then mark hasProblems = FALSE
camop_problem <- cameraOperation( CTtable = stat_dat_multi,
                      stationCol = "Station",
                      setupCol = "Date_Installed",
                      retrievalCol = "Date_Retrieved",
                      hasProblems = TRUE,
                      dateFormat = "ymd",
                      #we sterviced and installed cameras at 8am 
                      occasionStartTime = 8
                      
)



  #renaming stations from ind_recs_mod to get rid of the letter. Originally, we labeled every station as station 1, 1B, and 1C; 2, 2B, 2C; etc. to show the different treatments that each station would have gotten. For example, station 12 would be control, 12B would be PB, and 12C would be PB + fox. However, we ended up switching this method after having labeled them all as such, and now we want them to be just by their number (1-12) with no letter. This is because they should not be separate stations with letters as they are all technically the same station just with different treatments throughout the study, as represented by the letters (A, B, C). We annotated what the treatment type is in the treatment matrix later on in this multi-species occupancy analysis so it is ok to get rid of the letters here
  
ind_recs_multi <- ind_recs %>% 
  mutate(Station = gsub("(\\d+)[a-zA-Z].*", "\\1", Station))
```





## Summary Reports
```{r}

#creating summary reports. tables that just show broad info about species detected and stations 
report <- surveyReport(recordTable = ind_recs_multi,
                       CTtable = stat_dat_multi,
                       CTDateFormat = "ymd",
                       speciesCol = "Species",
                       setupCol = "Date_Installed",
                       retrievalCol = "Date_Retrieved",
                       recordDateTimeCol = "DateTimeOriginal")


report1 <- report$species_by_station 
report2 <- report$events_by_species
report3 <- report$events_by_station
```































### Detection History tables for each rodent species 
```{r}
## here we create detection history tables for each species. It can be a bit fickle doing this, so be patient if you get an error. Essentially this is creating data frames that show on what days for each station a rodent was observed (0,1) or NA if the camera was either 1) not set up during that dau, or 2) malfunctioned as indicated by the camera operation table.




############ woodrat ###################
woodrat_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_multi,
                        #camera operability table
                       camOp = camop_problem,
                       #what the species is 
                       species = "Woodrat",
                       #which column contains station
                       stationCol = "Station",
                       #which column contains species
                       speciesCol = "Species",
                       #dates time column and format. Format can be tricky. Refer to the 1st vignette                         included here in the project "vignettes" folder if you have a different format
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       # represented by 1 day or 24 hours
                       occasionLength = 1,
                       # this tells us that the trapping day goes from 8am on one day til 7:59am the                           next day. 
                       occasionStartTime = 8, 
                       day1 = "station",
                       includeEffort = FALSE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
                      #adding the station names from default column names
                      rownames_to_column("Station" ) 


# for some reason, camtrapR keeps adding an extra trapping day at the end of the matrix. It thinks that we trapped on 8/15/2023 but we took the cameras down that day. All records up until 8am on 8/15/2023 are included with the 8/14/2023 data after 8am, so there should be no data fro 8/15/23, but the detection history keeps making an extra column anyway. So I am removing that manually here. This may or may not be necessary for you 

# I am also making the row 13:24 of column 22 NA's because the same thing happened as previously described for our cameras 21-32 which are represented in rows 13-24. It seemse confusing, but this is the same step I did previously described, but for cameras 21-34 instead of 1-12.

# the reason that the extra days aren't all in 1 column is b/c cameras 1-12 were out for 25 days and cameras 21-32 were out for 21 days. Hence we have to remove false data from day (or column) 27 and 22



woodrat_hist <- woodrat_hist[, -c(1,27)] #removing column 1 (station names) and 27 which was the extra day for cameras 1-12 that was included which shouldnt be there
woodrat_hist[13:24, 22] <- NA #removing extra day for cameras 21-32



                                   ########## black rat #############
blackrat_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_multi,
                       camOp = camop_problem,
                       species = "Black rat",
                       stationCol = "Station",
                       speciesCol = "Species",
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       occasionLength = 1,
                       occasionStartTime = 8, 
                       day1 = "station",
                       includeEffort = FALSE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
  #adding the station names
  rownames_to_column("Station" ) 



blackrat_hist <- blackrat_hist[, -c(1,27)] 
blackrat_hist[13:24, 22] <- NA 






                               ############ mouse ################


mouse_hist <- as.data.frame(detectionHistory(recordTable = ind_recs_multi,
                       camOp = camop_problem,
                       species = "Mouse",
                       stationCol = "Station",
                       speciesCol = "Species",
                       recordDateTimeCol = "DateTimeOriginal",
                       recordDateTimeFormat = "%Y-%m-%d %H:%M:%S",
                       occasionLength = 1,
                       occasionStartTime = 8, 
                       day1 = "station",
                       includeEffort = FALSE,
                       scaleEffort = FALSE,
                       timeZone = "America/Los_Angeles"
                       # writecsv = TRUE,
                       # outDir = "/Users/rayhunter/Desktop/TNC/tnc_internship-/data"
                       )) %>% 
  #adding the station names
  rownames_to_column("Station" ) 

mouse_hist <- mouse_hist[, -c(1,27)]
mouse_hist[13:24, 22] <- NA



```





#### Preparing occupancy model 
```{r}


#### creating a combined list of detection history matrices for each species. detection histories MUST all be the same exact dimensions to work: there should be no station column, only observations. need to be matrices and NOT data frames   
y_list <-list(Woodrat = as.matrix(woodrat_hist),
              Blackrat = as.matrix(blackrat_hist),
              Mouse = as.matrix(mouse_hist)
              )

# creating a df of detection covariates (treatment). Need to get rid of rows with all NAs and station column 
 
treat_mx <- read.csv("data/treatment_detection_matrix_unmarked.csv")
#removing station names
det_covs <- data.frame(treat_mx[,-1])
#assigning NA values to the treatments that were applied on days in which the cameras were not working
det_covs[c(17,21), c(1:7)] <- NA 



#creating a list of detection covariates. Even though we only have one item, it still needs to be formatted as a list. If there were other detection covariates such as temperature or time of day we would also add those on here. Detection covariates are everything related to whether or not we might see a rodent given that it is present


det_list <- list(Treatment = as.matrix(det_covs))

#list of occupancy covariates: Here I am just drawing in all the habitat covariates such as % canopy, distance to water, etc. that are included in the occupancy (not detection) portion of the model. In other words, what variables may be determining whether or not a rodent occupies an area. This should essentially include your environmental data. 

occ_covs <- stat_dat_multi[, 5:11] 



# putting it all together in an unmarked Frame Multi-Species. Even though we use a Multi=species model, we arent looking at interactions BETWEEN species. We are looking at each species individually, so essentially 3 single species occupancy models. However, the unmarkedFrameOccuMulti() function allows you to include all 3 of the species in 1 model and look at them independently instead of running 3 separate models.


ufom_rods <- unmarkedFrameOccuMulti(y = y_list,
                                   siteCovs = occ_covs,
                                   obsCovs = det_list)


#scaling environmental covariate data. NOTE: this can only be done for numeric data (not character). This basically defines the range of the values for each variable in a more interpretable way for the model. 
ufom_rods@siteCovs$Percent_Canopy_Cover <- scale(ufom_rods@siteCovs$Percent_Canopy_Cover)
ufom_rods@siteCovs$Percent_Leaf_Litter <- scale(ufom_rods@siteCovs$Percent_Leaf_Litter)
ufom_rods@siteCovs$Percent_Bare <- scale(ufom_rods@siteCovs$Percent_Bare)
ufom_rods@siteCovs$Percent_Woody_Debris <- scale(ufom_rods@siteCovs$Percent_Woody_Debris)
ufom_rods@siteCovs$Distance_to_Water_.m. <- scale(ufom_rods@siteCovs$Distance_to_Water_.m.)
ufom_rods@siteCovs$Distance_to_Building_.m. <- scale(ufom_rods@siteCovs$Distance_to_Building_.m.)





```


### Making Multi-Species Models: changes in log-odds 
```{r}


### here we are creating the models. It can be a bit confusing so stay with me. I recommend watching this entire tutorial as it explains what is going on here:

##.   https://www.youtube.com/watch?v=tj_OCO77_sc


#Essentially, we are fitting the data to each of the assigned predictor variables. We take the variables of interest and assign them to each species. For example model 1 looks like this:

# detformulas = c('~1', '~1', '~1'),
# stateformulas = c('~1', '~1', '~1'),

# detformula is where you enter the detection variables and stateformula is where you enter occupancy variables. In this case, we put 1 for all of them. So no predictor variables were applied

#in other models you will see something like 
# detformulas = c('~Treatment', '~Treamtent', '~Treatment'),
# stateformulas = c('~Distance to Building', '~Distance to Building', '~Distance to Water'),

# the order of the values separated by the comas is the same as the order of the species entered in the y_list portion the occuFrameMulti. For example, I included woodrat first, black rat second, and mouse third in the y_list. This means that the detformula and stateformula follow the same order. ~1 for woodrat, ~1 black rat, and ~1 mouse. Another example:  model 7 (see below) would be such for the state formula: 

# ~ Distance_to_Water_.m. ( for woodrat)', '~  Distance_to_Building_.m. (for black rat)', '~ 1 (for mouse)'

# Order matters. 


# so lets get into it!



###################### model 1 ###########################




### intercept only model but assuming independence of species. This model basically implies that nothing is responsble for detection and occupancy 

fit_1m <- occuMulti(detformulas = c('~1', '~1', '~1'),
                    stateformulas = c('~1', '~1', '~1'),
                    maxOrder = 1,
                    data = ufom_rods)
#run the summary below to see what the model output and significance is
# # summary(fit_1m)





###################### model 2 ###########################

### intercept only model but assuming dependence of species
# allowing second order natural parameters maxOrder = 2. This model looks at interactions BETWEEN speceis as indicated by the secod row of state formulas. We arent looking at this in this study, but I just wrote it out here to show it

fit_2m <- occuMulti(detformulas = c('~1', '~1', '~1'),
                    stateformulas = c('~1', '~1', '~1',
                                      '~1', '~1', '~1'),
                    maxOrder = 2,
                    data = ufom_rods)

# # summary(fit_2m)


###################### model 3 ###########################
## more complex model with treatment as detection variable and other variables for each species
fit_3m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~Habitat + Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover + Percent_Woody_Debris', '~Habitat + Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover + Percent_Woody_Debris', '~Habitat + Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover + Percent_Woody_Debris'),
                    maxOrder = 1,
                    data = ufom_rods)
#
# # summary(fit_3m)


###################### model 4 ###########################

fit_4m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover', '~Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover', '~Distance_to_Water_.m. + Distance_to_Building_.m. + Percent_Canopy_Cover'),
                    maxOrder = 1,
                    data = ufom_rods)
#
# # summary(fit_4m)


###################### model 5 ###########################

fit_5m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~Distance_to_Building_.m.', '~  Distance_to_Building_.m. ', '~ Distance_to_Water_.m.'),
                    maxOrder = 1,
                    data = ufom_rods)


# summary(fit_5m)

###################### model 6 ###########################


fit_6m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~ Percent_Woody_Debris ', '~  Distance_to_Building_.m. + Percent_Canopy_Cover ', '~ Percent_Woody_Debris'),
                    maxOrder = 1,
                    data = ufom_rods)


# summary(fit_6m)


###################### model 7 ###########################

fit_7m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~ Distance_to_Water_.m. ', '~  Distance_to_Building_.m. ', '~ 1'),
                    maxOrder = 1,
                    data = ufom_rods)


summary(fit_7m)


###################### model 8 ###########################


fit_8m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~ 1', '~  Habitat  ', '~ 1'),
                    maxOrder = 1,
                    data = ufom_rods)


# summary(fit_8m)

###################### model 9 ###########################

fit_9m <- occuMulti(detformulas = c('~Treatment', '~Treatment', '~Treatment'),
                    stateformulas = c('~1', '~  1', '~ 1'),
                    maxOrder = 1,
                    data = ufom_rods)


# summary(fit_9m)



```




### Model Selection 
```{r}
#looking at AIC values for all models
AIC(fit_1m, fit_2m, fit_3m, fit_4m, fit_5m, fit_6m, fit_7m, fit_8m, fit_9m)
#creating a vector of AIC values for the top 3 models 
aic_values <- AIC(fit_6m, fit_7m, fit_5m)
# creating a vector of log liklihood for each of the 3 models 
logLiklihood <- c(logLik(fit_6m), logLik(fit_7m), logLik(fit_5m))
# creating a vector of the number of coefficients or parameters for each of the 3 models 
params <- c(length(coef(fit_6m)), length(coef(fit_7m)), length(coef(fit_5m)))


# adding this all togther to make a model selection data frame 
aic_tab <- data.frame(
  #naming each model 
  Model = c("Model 6", "Model 7", "Model 5"),
  #writing out the definition of each model where p is detection probability and psi is occupancy
 Model_definition = c("p ~ Treatment, Treatment, Treatment; psi ~ Woody_Debris,  Distance to Building + Canopy_Cover, WoodyDebris", "p ~ Treatment, Treatment, Treatment; psi~ Distance_to_Water, Distance_to_Building, 1", "p ~ Treatment, Treatment, Treatment; psi ~ Distance_to_Building, Distance_to_Building, Distance_to_Water"),
 #parameters for each model
Parameters = params,
#log liklihood 
Log_liklihood = logLiklihood,
#aic values
aic_values,
# calculating delta AIC 
Delta_AIC = aic_values$AIC - min(aic_values$AIC),
# calculating AIC weights
AIC_weights = Weights(aic_values))



#after inspecting, you can see model 6 is the best (lowest AIC) 

#writing a csv file for export
write.csv(aic_tab, file = "data/aic_table.csv", row.names = FALSE)
```


### Effect Size
```{r}
#df with sumamry results from best model 
m6_results <- summary(fit_6m)

## making a df that shows the chosen model outputs and effect size 
det_res_m6 <- as.data.frame(m6_results$det) %>% 
  #making treat
rownames_to_column("Treatment" ) %>% 
  mutate(Species = rep(c("Woodrat", "Black rat", "Mouse"), 
                       each = 4)) %>% 
  mutate(Treatment = rep(c("Intercept", "Control", "PB", "PB + Fox"), length.out = 12)) %>% 
  # we dont want to see effect size of intercept of control 
  filter(Treatment != c("Intercept", "Control")) 
  
  




### effect size figure 
eff_plot <- ggplot(det_res_m6, aes(x = Species, y = Estimate,  color = Treatment)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.2,  position = position_dodge(width = 0.4)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
  labs(
       x = "Species",
       y = "Lure Effect Size") +
   # ylim(-1.5, 1.5) + 
  theme_minimal() +
  scale_color_manual(values = c("PB" = "#1f77b4", "PB + Fox" = "#2ca02c")) +
  scale_y_continuous(limits = c(-.5, 1.25), expand = c(0, 0)) +  # Start y-axis at 0 and limit to 0-1
  theme(plot.title = element_text(size = 16, margin = margin(0,0,30,0)),
        axis.title = element_text(size = 13),
        axis.title.x = element_text(margin = margin(t = 10)),  # Increase x-axis title margin
        axis.title.y = element_text(margin = margin(r = 10)),  # Increase y-axis title margin
        axis.text.x = element_text(margin = margin(t = 5)),    # Increase x-axis tick label margin
        axis.text.y = element_text(margin = margin(r = 5)),   # Increase y-axis tick label margin)
        axis.line = element_line(color = "black", size = .5),  # Add black axis line
        axis.ticks = element_line(color = "black", size = .5))

eff_plot

ggsave("figures/eff_plot.jpeg", plot = eff_plot, width = 6, height = 4, dpi = 300)

```



###### Using models to predict 
```{r}
## making a prediction model data frame that we can use to predict the detection probability with 
# we hold the environemtal variables constant at their average as we are interested in the average treatment prediction 
preds <- data.frame(
  # Species = rep(c("Woodrat", "Black rat ", "Mouse"), length.out = 3),
  Treatment = rep(c("control", "PB", "PB + fox"), length.out = 3),
  Distance_to_Building_.m. = rep(mean(occ_covs$Distance_to_Building_.m.), 3),
  Distance_to_Water_.m. = rep(mean(occ_covs$Distance_to_Water_.m.), 3)
)



#predicting detection probability across treatments 
wr_preds <- predict(fit_7m, type = "det", species = "Woodrat", newdata = preds)
br_preds <- predict(fit_7m, type = "det", species = "Blackrat", newdata = preds)
m_preds <- predict(fit_7m, type = "det", species = "Mouse", newdata = preds)


#adding up the preds together 
comb_preds <- rbind(wr_preds, br_preds, m_preds)


#data frame containing prediciton output so we can graph it 
preds_fig <- data.frame(
  Species = rep(c("Woodrat", "Black rat ", "Mouse"), each = 3),
  Treatment = rep(c("Control", "PB", "PB + fox"), length.out = 3),
  det_prob = comb_preds$Predicted,
  low = comb_preds$lower,
  high = comb_preds$upper
)
preds_fig
```






### makign a plot for predicitons 
```{r, fig.cap = "test"}
my_colors <- c("#1f77b4", "#ff7f0e", "#2ca02c")


det_plot <- ggplot(preds_fig, aes(x = Treatment, y = det_prob, group = Species, color = Species)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 0.2,  position = position_dodge(width = 0.4)) +
  labs(
       x = "Treatments",
       y = "Daily Detection Probability") +
   ylim(0, 1) + 
  theme_minimal() +
  scale_color_manual(values = my_colors) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +  # Start y-axis at 0 and limit to 0-1
  theme(plot.title = element_text(size = 16, margin = margin(0,0,30,0)),
        axis.title = element_text(size = 13),
        axis.title.x = element_text(margin = margin(t = 10)),  # Increase x-axis title margin
        axis.title.y = element_text(margin = margin(r = 10)),  # Increase y-axis title margin
        axis.text.x = element_text(margin = margin(t = 5)),    # Increase x-axis tick label margin
        axis.text.y = element_text(margin = margin(r = 5)),   # Increase y-axis tick label margin)
        axis.line = element_line(color = "black", size = .5),  # Add black axis line
        axis.ticks = element_line(color = "black", size = .5))

det_plot


ggsave("figures/det_plot.jpeg", plot = det_plot, width = 6, height = 4, dpi = 300)


```















































